VIP-193: Committee-Based POA

### 2019-11-12 article.tex
add assumptions

\section{Overview}
The Proof-of-Authority consensus algorithm~\cite{VWP18}, or POA in short, is efficient of using network bandwidth. It divides time into rounds with a fixed length and assumes that the majority of its (authorized) nodes perform consensus in the same round.

In each round, nodes select a leader (the node responsible for generating a new block) based on the round number, block height and their local views of active nodes. Therefore, the procedure can be considered instant, which allows more time for transmitting transaction (TX) data in each consensus round.

@@

\section{Specifications}
\subsection{Notations}
\renewcommand{\arraystretch}{2}
\begin{longtable}{p{3cm} p{10cm}}
    Symbol  & Description \\
    \hline\hline
    $N$ & Total number of nodes \\
    \hline
    $u=1,2,\dots,N$ & node index \\
    \hline
    $H(\cdot)$ & Cryptographic hash function \\
    \hline
    ${\tt SIG}_u(\cdot)$ & Signature of $u$ \\
    \hline
    ${\tt PK}_u$ & Public key of $u$ \\
    \hline
    ${\tt SK}_u$ & Private key of $u$ \\
    \hline
    $\rho\left(\cdot\right)$ & Merkle root of the input set\\
    \hline
    $r$ & Consensus round number \\
    \hline
    $l_r=1,2,...,N$ & Leader in round $r$ \\
    \hline
    $s_r$ & Block summary produced by $l_r$ \\
    \hline
    $\tau_r$ & $s_r\,\|\,{\tt Sig}_{\,l_r}(s_r)$ \\
    \hline
    $\epsilon$ & Predefined threshold to determine committee memberships \\
    \hline
    $d$ & Number of endorsements required for forming a valid block \\
    \hline
    $\Sigma_r$ & Pending transaction set prepared by $l_r$ \\
    \hline
    $B_{u,r}^*$ & Last block of the canonical chain recognized by $u$ in round $r$\\ 
    \hline
    $H_{vrf},\Pi_{vrf},V_{vrf}$ & Functions that compute hash, generate proof and verify proof defined in the VRF scheme, respectively \\
    \hline
    ${\tt M}_{\,r}$ & Common VRF message generated for committee selection \\
    \hline
    $\omega$, $\omega^*$ & Branch and trunk \\
    \hline
    $m$, $L$ & Epoch number and the number of consensus rounds in one epoch \\
    \hline
    $b_m$ & Random beacon computed using randomness from the last block of the $m$'th epoch \\
    \hline
\end{longtable}

@@

\subsection{Double-Spending Attack}
The main goal of introducing the committee mechanism is to make it more difficult for adversaries to cause inconsistency. Perhaps the most damaging of such attacks is the double-spending attacks~(DSAs)~\cite{Sat08} where adversaries are allowed to take control of a few consecutive consensus rounds such that they can produce two parallel branches to launch a DSA. Here we are going to infer a lower bound for the probability of launching a $k$-block DSA. We focus on solving the DSA in a practical synchronous network setting, where we assume that a message be broadcast through the gossip protocol and reach the whole network with some bounded delay.

@@

where $c$ is the total number of committee-member signatures the leader receives. Table~\ref{tab:dsa-prob} below provides some example of the probabilities of launching a DSA.

>>>>

\section{Overview}
The Proof-of-Authority consensus algorithm~\cite{VWP18}, or POA in short, is efficient of using network bandwidth. It divides time into rounds with a fixed length and assumes that the majority of its (authorized) nodes perform consensus in the same round. In each round, nodes select a leader (the node responsible for generating a new block) based on the round number, block height and their local views of active nodes. Therefore, the procedure can be considered instant, which allows more time for transmitting transaction (TX) data in each consensus round.

@@

We assume that the network is synchronous and the messages are transmitted through gossip communication, i.e., if an honest node sends a message or an honest node receives a message, all other honest nodes will receive same message within at most a delay of $\tau$, which is determined by the network configuration and known in advance.

%Note that besides the network synchrony, we also assume that messages be transmitted through gossip communication. Hence, if an honest node receives a message, all other honest nodes will receive the same message with a bounded delay. 
\section{Specifications}
\subsection{Notations}
\renewcommand{\arraystretch}{2}
\begin{longtable}{p{3cm} p{10cm}}
    Symbol  & Description \\
    \hline\hline
    $N$ & Total number of nodes \\
    \hline
    $u=1,2,\dots,N$ & node index \\
    \hline
    $H(\cdot)$ & Cryptographic hash function \\
    \hline
    ${\tt SIG}_u(\cdot)$ & Signature of $u$ \\
    \hline
    ${\tt PK}_u$ & Public key of $u$ \\
    \hline
    ${\tt SK}_u$ & Private key of $u$ \\
    \hline
    $\rho\left(\cdot\right)$ & Merkle root of the input set\\
    \hline
    $r$ & Consensus round number \\
    \hline
    $l_r=1,2,...,N$ & Leader in round $r$ \\
    \hline
    $s_r$ & Block summary produced by $l_r$ \\
    \hline
    $\tau_r$ & $s_r\,\|\,{\tt Sig}_{\,l_r}(s_r)$ \\
    \hline
    $\epsilon$ & Predefined threshold to determine committee memberships \\
    \hline
    $d$ & Number of endorsements required for forming a valid block \\
    \hline
    $\Sigma_r$ & Pending transaction set prepared by $l_r$ \\
    \hline
    $B_{u,r}^*$ & Last block of the canonical chain recognized by $u$ in round $r$\\ 
    \hline
    $H_{vrf},\Pi_{vrf},V_{vrf}$ & Functions that compute hash, generate proof and verify proof defined in the VRF scheme, respectively \\
    \hline
    ${\tt M}_{\,r}$ & Common VRF message generated for committee selection \\
    \hline
    $\omega$, $\omega^*$ & Branch and trunk \\
    \hline
    $m$, $L$ & Epoch number and the number of consensus rounds in one epoch \\
    \hline
    $b_m$ & Random beacon computed using randomness from the last block of the $m$'th epoch \\
    \hline
\end{longtable}

@@

\subsection{Double-Spending Attack}
The main goal of introducing the committee mechanism is to make it more difficult for adversaries to cause inconsistency. Perhaps the most damaging of such attacks is the double-spending attacks~(DSAs)~\cite{Sat08} where adversaries are allowed to take control of a few consecutive consensus rounds such that they can produce two parallel branches to launch a DSA. Here we are going to infer a lower bound for the probability of launching a $k$-block DSA.

@@

where $c$ is the total number of committee-member signatures the leader receives. Table~\ref{tab:dsa-prob} below provides some examples of the probabilities of launching a DSA.
